ACNP 2024 MS ANXIETY

### 2024-08-13 MSAnxiety_manuscript_audrey_replication.Rmd
Add files via upload

#### Plot promis x anxiety dose, group by mental vs physical health
```{r plot_Promis_x_anxiety}
#set mood versus physical domains
mood_domains <- c("Quality_of_Life", 
                "Mental_Health_and_Mood",
                "Social_Activities_Satisfaction",
                "Carrying_Out_Social_Activities",
                "Emotional_Problems", 
                "PostOp.PROMIS.Mental.Score")

>>>>

#### Plot promis x anxiety dose, group by mental vs physical health
```{r plot_Promis_x_anxiety}
#set mood versus physical domains
mood_domains <- c("Mental_Health_and_Mood",
                "Social_Activities_Satisfaction",
                "Carrying_Out_Social_Activities",
                "Emotional_Problems", 
                "Quality_of_Life",
                "PostOp.PROMIS.Mental.Score")
